prolfqua&colon; A Comprehensive R-package for Proteomics Differential Expression Analysis

### 2024-06-28 inst/MyArticle/paper.Rmd
create benchpath with date

## read MQ peptide.txt and annotation table
startdata <- prolfquapp::tidyMQ_Peptides(system.file(
  "samples/maxquant_txt/tiny2.zip", package = "prolfqua"))
annot <- readxl::read_xlsx(system.file(
  "samples/maxquant_txt/annotation_Ionstar2018_PXD003881.xlsx", package = "prolfqua"))
startdata <- dplyr::inner_join(annot, startdata, by = "raw.file")

## create MaxQuant configuration
config <- prolfqua::create_config_MQ_peptide()

## specify explanatory variable
config$table$factors[['dilution.']] = "sample"

## create R6 object
lfqpep <- prolfqua::LFQData$new(startdata, config, setup = TRUE)

@@

```{r figure2, fig.cap="(ref:figure2)", echo=TRUE, out.width = '90%', fig.width = 8, fig.height = 5}
## specify differences among groups
contrasts <- c(
  "e_vs_d" =   "dilution.e - dilution.d",
  "d_vs_c" =   "dilution.d - dilution.c"
)
## fit model
lmmodel <- paste(lfqpro$response()," ~ dilution.")
modelFunction <- prolfqua::strategy_lm( lmmodel, model_name = "lm")
models <- prolfqua::build_model(lfqpro, modelFunction)

>>>>

## read MQ peptide.txt and annotation table
startdata <- prolfqua::sim_lfq_data_peptide_config(Nprot = 100)

## create R6 object
lfqpep <- prolfqua::LFQData$new(startdata$data, startdata$config, setup = FALSE)

@@

```{r figure2, fig.cap="(ref:figure2)", echo=TRUE, out.width = '90%', fig.width = 8, fig.height = 5}
## specify differences among groups
contrasts <- c(
  "a_vs_c" =   "group_A - group_Ctrl",
  "b_vs_c" =   "group_B - group_Ctrl"
)
## fit model
lmmodel <- paste(lfqpro$response()," ~ group_")
modelFunction <- prolfqua::strategy_lm( lmmodel, model_name = "lm")
models <- prolfqua::build_model(lfqpro, modelFunction)
